---
title       : Confidence Intervals
description : Big ideas of confidence intervals (estimation instead of testing).  We'll switch to one proportion for ease in interpretation.  Focus on foundational ideas, not specific details

--- type:VideoExercise lang:r xp:50 skills:1
## Confidence Intervals

Introduction to the idea of confidence intervals.  Focus on the idea of wanting to know the parameter.  Example about the presidential election.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1
## What is the parameter?

Using the current presidential election - 6 months prior!!  We get to talk about so many good aspects of understanding parameters.

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1
## Re-sampling from a sample - tiny n

Notice that the variability in p-hat is HUGE

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Re-sampling from a sample - big n

Notice that the variability in p-hat is non-existent

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Re-sampling from a sample - same n

Notice that we get variability in p-hat that seems reasonable

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1
## Variability in p-hat

Discuss their normal exercises.  Maybe also talk about SE(phat) = sqrt(p(1-p)/n)... or at least that we know a formula which works well a lot of the time. Then the big important point is that true p is as far from p-hat as p-hat is from true p.  Measured by exactly the variability we just saw.  Also, show Empirical Rule.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1
## Empirical Rule

Have them find the SE of the resampled phats

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Empirical Rule

Have them find the values for 95% of phats  (or resampled phats?)

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## t-Confidence Interval

Have them actually make the CI

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1
## Interpreting CIs and technical conditions

Discuss the interval they made and what it says about the parameter.  Then discus how the process works for any statistic/parameter pair when the technical conditions are met.  State technical conditions and refer to later in the course (averages) for more details.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1
## Sample size effects CI

Repeat process of finding CI for smaller / larger sample sizes

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Sample proportion value effects CI

Repeate process of finding CI for different values of the sample proportion (not much change here!)

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Confidence level effects CI

Repeate process of finding CI for different values of the confidence level

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1
## Summary of Statistical Inference / Estimation

Summary of Statistical Inference / Estimation

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

