---
title       : "Completing a Randomization Test: gender discrimination"
description : Now focusing on a specific example, the student will run the randomization test on their own.

--- type:VideoExercise lang:r xp:50 skills:1 key:6043a3029d
## Example: gender discrimination

Introduction of the example and the scientific question.

We consider a study investigating gender discrimination in the 1970s, which is set in the
context of personnel decisions within a bank. The research question we hope to answer is,
``Are females discriminated against in promotion decisions made by male managers?"

(citation: Rosen B and Jerdee T. 1974. Influence of sex role stereotypes on personnel decisions. Journal of Applied Psychology 59(1):9-14.)


The participants in this study were 48 male bank supervisors attending a management
institute at the University of North Carolina in 1972. They were asked to assume the role
of the personnel director of a bank and were given a personnel file to judge whether the
person should be promoted to a branch manager position. The files given to the participants were identical, except that half of them indicated the candidate was male and the other half indicated the candidate was female. These files were randomly assigned to the subjects.

In this study, a smaller proportion of females are promoted than males (0.583 versus 0.875), but it is unclear whether the difference provides convincing evidence that females are unfairly discriminated against.

\begin{tabular}{lccr}
\hline
& promoted & not promoted & Total
\hline
male & 21 &3 & 24\\
female & 14 & 10 & 24\\
\hline
Total & 35 & 13 & 48\\
\hline
\end{tabular}
Table: Summary results for the gender discrimination study.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:2a7a6e7a00
## Gender discrimination hypotheses

Which are the null and alternative hypotheses related to the example?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1 key:c4d9027dcd
## Summarizing gender discrimination

Calculating summary statistics, prop(), perc()

note that it's important to think about the denominator.  That is, percent of what?  Do we want to calclulate the percent of women who were promoted?  Or the percent of people who were promoted that are women?

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
library(dplyr)
GendDiscr <- data.frame(promote = c(rep('promoted',35),rep('not_promoted',13)),
  sex = c(rep('male',21), rep('female',14), rep('male',3), rep('female',10)))
```

*** =sample_code
```{r}

GendDiscr %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted")) %>%
  mutate(perc_prom = 100*prop_prom)

```

*** =solution
```{r}
# solution code
GendDiscr %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted")) %>%
  mutate(perc_prom = 100*prop_prom)
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:7dabb1c285
## Randomizing gender discrimination

create a randomization distribution of the statistic which is the difference in proportions

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
library(dplyr)

GendDiscr %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom_perm = mean(promote_perm == "promoted")) 
```

*** =sample_code
```{r}
# sample code
set.seed(47)
shuffpromote <- mosaic::do(10000)*GendDiscr %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female
 

ggplot(shuffpromote, aes(x=prop_prom_perm)) + geom_histogram() +
  geom_vline(aes(xintercept=prop_prom), col="red")
```

*** =solution
```{r}
# solution code

set.seed(47)
shuffpromote <- mosaic::do(10000)*GendDiscr %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1 key:214ddc88d0
## Distribution of statistics

Discussion of how the difference in proportions was chosen.  Talk about sample size as it impacts variability and how different sample sizes would make comparing number of successes as meaningless.  Also how, generally, there are lots of statistics that would lead to a complete analysis.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:5b526ccd1f
## Reflecting on analysis

Given the statistic they calculated and the distribution the created, what do they think of the conclusion?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1 key:43f7f4be76
## Critical Region

quantile() to figure out different critical regions

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec

set.seed(47)
shuffpromote <- mosaic::do(10000)*GendDiscr %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female

```

*** =sample_code
```{r}
# sample code

shuffpromote %>% summarise(q.9 = quantile(prop_prom_perm, p=0.9),
                           q.95 = quantile(prop_prom_perm, p=0.95),
                           q.99 = quantile(prop_prom_perm, p=0.99))
```

*** =solution
```{r}
# solution code

shuffpromote %>% summarise(q.9 = quantile(prop_prom_perm, p=0.9),
                           q.95 = quantile(prop_prom_perm, p=0.95),
                           q.99 = quantile(prop_prom_perm, p=0.99))

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:8177755245
## Two-sided critical Region

exercise to get them thinking about the other side of the distribution and that it isn't relevant in this scenario

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
set.seed(47)
shuffpromote <- mosaic::do(10000)*GendDiscr %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female

shuffpromote %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())
```

*** =sample_code
```{r}
# sample code

shuffpromote %>% summarise(q.01 = quantile(prop_prom_perm, p=0.01),
                           q.05 = quantile(prop_prom_perm, p=0.05),
                           q.1 = quantile(prop_prom_perm, p=0.1))
```

*** =solution
```{r}
# solution code

shuffpromote %>% summarise(q.01 = quantile(prop_prom_perm, p=0.01),
                           q.05 = quantile(prop_prom_perm, p=0.05),
                           q.1 = quantile(prop_prom_perm, p=0.1))
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1 key:19c768bc6f
## Why 0.05?

www.openintro.org/why05

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:b76dc95b72
## How does sample size affect results?

With a .05 cutoff, how big would the observed result have to be to reject H0 GIVEN changes in sample size.

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1 key:4790473486
## Sample size in randomization distribution

Vary the sample size to calculate 4 different randomization distributions

I know this is too long... but the code is all the same as before.  What do I do here??

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec

library(tidyr)
GendDiscr.d3 <- data.frame(promote = c(rep('promoted',12),rep('not_promoted',4)),
  sex = c(rep('male',7), rep('female',5), rep('male',1), rep('female',3)))

# am I allowed to use tidyr::spread?  If not, any ideas on simple tabulation?
GendDiscr.d3 %>% 
  count(sex, promote) %>%
  spread(promote, n)

GendDiscr.m10 <- data.frame(promote = c(rep('promoted',350),rep('not_promoted',130)),
  sex = c(rep('male',210), rep('female',140), rep('male',30), rep('female',100)))

GendDiscr.m10 %>% 
  count(sex, promote) %>%
  spread(promote, n)

```

*** =sample_code
```{r}
# sample code


set.seed(47)
shuffpromote.d3 <- mosaic::do(10000)*GendDiscr.d3 %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female

ggplot(shuffpromote.d3, aes(x=prop_prom_perm)) + geom_histogram() +
  geom_vline(aes(xintercept=prop_prom), col="red")

set.seed(47)
shuffpromote.m10 <- mosaic::do(10000)*GendDiscr.m10 %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female

ggplot(shuffpromote.m10, aes(x=prop_prom_perm)) + geom_histogram() +
  geom_vline(aes(xintercept=prop_prom), col="red")


```

*** =solution
```{r}
# solution code
set.seed(47)
shuffpromote.d3 <- mosaic::do(10000)*GendDiscr.d3 %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female

ggplot(shuffpromote.d3, aes(x=prop_prom_perm)) + geom_histogram() +
  geom_vline(aes(xintercept=prop_prom), col="red")

set.seed(47)
shuffpromote.m10 <- mosaic::do(10000)*GendDiscr.m10 %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female

ggplot(shuffpromote.m10, aes(x=prop_prom_perm)) + geom_histogram() +
  geom_vline(aes(xintercept=prop_prom), col="red")

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:5124699651
## Sample size for critical region

Using the randomization distributions with different sample sizes, calculate different cutoffs for significance

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
shuffpromote %>% summarise(q.9 = quantile(prop_prom_perm, p=0.9),
                           q.95 = quantile(prop_prom_perm, p=0.95),
                           q.99 = quantile(prop_prom_perm, p=0.99))


shuffpromote.d3 %>% summarise(q.9 = quantile(prop_prom_perm, p=0.9),
                           q.95 = quantile(prop_prom_perm, p=0.95),
                           q.99 = quantile(prop_prom_perm, p=0.99))


shuffpromote.m10 %>% summarise(q.9 = quantile(prop_prom_perm, p=0.9),
                           q.95 = quantile(prop_prom_perm, p=0.95),
                           q.99 = quantile(prop_prom_perm, p=0.99))


```

*** =solution
```{r}
# solution code

shuffpromote %>% summarise(q.9 = quantile(prop_prom_perm, p=0.9),
                           q.95 = quantile(prop_prom_perm, p=0.95),
                           q.99 = quantile(prop_prom_perm, p=0.99))


shuffpromote.d3 %>% summarise(q.9 = quantile(prop_prom_perm, p=0.9),
                           q.95 = quantile(prop_prom_perm, p=0.95),
                           q.99 = quantile(prop_prom_perm, p=0.99))


shuffpromote.m10 %>% summarise(q.9 = quantile(prop_prom_perm, p=0.9),
                           q.95 = quantile(prop_prom_perm, p=0.95),
                           q.99 = quantile(prop_prom_perm, p=0.99))

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1 key:6590b3f701
## What is a p-value?

Bringing together the ideas they've worked through above with the definition of a p-value.  The p-value measures the degree of disagreement between the data and the null hypothesis.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1 key:c5627bce8e
## Calculating THE p-values

have them do the actual p-value calculation that brings together all the pieces above

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code

shuffpromote %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())

shuffpromote.d3 %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())

shuffpromote.m10 %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())

```

*** =solution
```{r}
# solution code
shuffpromote %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())

shuffpromote.d3 %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())

shuffpromote.m10 %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:59076280e6
## Calculating p-values

calculate the p-value given a randomization distribution(s) (made up, different from gender data)

the idea here is to think about what that distribution would look like with totally different data.

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
library(tidyr)
GendDiscr.new <- data.frame(promote = c(rep('promoted',35),rep('not_promoted',13)),
  sex = c(rep('male',28), rep('female',7), rep('male',10), rep('female',3)))

GendDiscr.new %>% 
  count(sex, promote) %>%
  spread(promote, n)

GendDiscr.new %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted")) 

set.seed(47)
shuffpromote.new <- mosaic::do(10000)*GendDiscr.new %>%
  mutate(promote_perm = sample(promote)) %>%
  group_by(sex) %>%
  summarize(prop_prom = mean(promote == "promoted"),
            prop_prom_perm = mean(promote_perm == "promoted")) %>%
  select(-sex) %>%
  sapply(diff) # Male - Female


```

*** =sample_code
```{r}
# sample code

ggplot(shuffpromote, aes(x=prop_prom_perm)) + geom_histogram() +
  geom_vline(aes(xintercept=prop_prom), col="red")

ggplot(shuffpromote.new, aes(x=prop_prom_perm)) + geom_histogram() +
  geom_vline(aes(xintercept=prop_prom), col="red")

shuffpromote %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())

shuffpromote.new %>%
 dplyr::summarise(sum(prop_prom < prop_prom_perm) / n())

```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:6e75cbd833
## Calculating two-sided p-values

calculate a two-sided p-value given a randomization distribution(s) (differential promotion rates)

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
shuffpromote %>%
 dplyr::summarise(2*sum(prop_prom < prop_prom_perm) / n())
```

*** =solution
```{r}
# solution code
shuffpromote %>%
 dplyr::summarise(2*sum(prop_prom < prop_prom_perm) / n())

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1 key:7bf3a36164
## Summary of gender discrimination

Summarize what we can say about gender discrimination.  Note that we are given a randomized study, so it makes sense to infer causal conclusions.  It is not, however, a random sample from the population, so we should be wary of concluding back to a larger population.  Additionally, the p-value is 0.02 which is thought of to be moderately significant and not extremely significant.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

