---
title       : "Hypothesis testing Errors: opportunity cost"
description : We will continue with a new example and the same structure of creating a randomization test.  Here, however, the focus will be on different errors (type I and type II), how they are made, when one is worse than another, and how things like sample size and effect size affect the error rates.

--- type:VideoExercise lang:r xp:50 skills:1
## Example: opportunity cost

Introduction to the example, layout of the data, research question, tactile simulation via cards (?)

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1
## Summarizing opportunity cost

Calculating summary statistics, prop(), perc()

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Plotting opportunity cost

Barchart for the data

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Randomizing opportunity cost

create a randomization distribution of the statistic which is the difference in proportions

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Summarizing opportunity cost

using the randomization distribution, compute the p-value

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:MultipleChoiceExercise lang:r xp:50 skills:1
## Opportunity cost conclusion

What can we conclude (in words) given the analysis?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:VideoExercise lang:r xp:50 skills:1
## Errors and their consequences

Discussion of errors, how we make statistical conclusions (control type I error), our knowledge of which error comes from our decision not from truth (which we can't ever know)

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1
## Different choice of error rate

What if we never want to make a type II error, what is our decision?  (Never reject)

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:MultipleChoiceExercise lang:r xp:50 skills:1
## Errors for two-sided hypotheses

What are type I and type II errors for the TWO-sided hypotheses related to the opportunity costs example

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1
## p-value for two-sided hypotheses: opportunity costs

compute the p-value for two-sided hypotheses, first compute the p-value for one tail of the distribution, then double that value to get the two-sided p-value. That's it!

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1
## Hypotheses should be set *before* seeing data

Discussion / simulation on why we need to set the hypotheses first

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1
## Error rates when snooping

Have them simulate data with snooping to see that their type I error rate doubles if testing two sided

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

