---
title       : "Completing a Randomization Test: gender discrimination"
description : Now focusing on a specific example, the student will run the randomization test on their own.

--- type:VideoExercise lang:r xp:50 skills:1
## Example: gender discrimination

Introduction of the example and the scientific question.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1
## Gender discrimination hypotheses

Which are the null and alternative hypotheses related to the example?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1
## Summarizing gender discrimination

Calculating summary statistics, prop(), perc()

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Randomizing gender discrimination

create a randomization distribution of the statistic which is the difference in proportions

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1
## Distribution of statistics

Discussion of how the difference in proportions was chosen.  Talk about sample size as it impacts variability and how different sample sizes would make comparing number of successes as meaningless.  Also how, generally, there are lots of statistics that would lead to a complete analysis.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1
## Reflecting on analysis

Given the statistic they calculated and the distribution the created, what do they think of the conclusion?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1
## Critical Region

quantile() to figure out different critical regions

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Two-sided critical Region

exercise to get them thinking about the other side of the distribution and that it isn't relevant in this scenario

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1
## Why 0.05?

www.openintro.org/why05

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1
## How does sample size affect results?

With a .05 cutoff, how big would the observed result have to be to reject H0 GIVEN changes in sample size.

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1
## Sample size in randomization distribution

Vary the sample size to calculate 4 different randomization distributions

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Sample size for critical region

Using the randomization distributions with different sample sizes, calculate different cutoffs for significance

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1
## What is a p-value?

Bringing together the ideas they've worked through above with the definition of a p-value.  The p-value measures the degree of disagreement between the data and the null hypothesis.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1
## Calculating THE p-values

have them do the actual p-value calculation that brings together all the pieces above

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Calculating p-values

calculate the p-value given a randomization distribution(s) (made up, different from gender data)

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1
## Calculating two-sided p-values

calculate a two-sided p-value given a randomization distribution(s) (made up, different from gender data)

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1
## Summary of gender discrimination

Summarize what we can say about gender discrimination.  Note that we are given a randomized study, so it makes sense to infer causal conclusions.  It is not, however, a random sample from the population, so we should be wary of concluding back to a larger population.  Additionally, the p-value is 0.02 which is thought of to be moderately significant and not extremely significant.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

