---
title       : "Hypothesis testing Errors: opportunity cost"
description : We will continue with a new example and the same structure of creating a randomization test.  Here, however, the focus will be on different errors (type I and type II), how they are made, when one is worse than another, and how things like sample size and effect size affect the error rates.

--- type:VideoExercise lang:r xp:50 skills:1 key:e86e653f0a
## Example: opportunity cost

Introduction to the example, layout of the data, research question, tactile simulation via cards (?)


How rational and consistent is the behavior of the typical American college student? In this section, we'll explore whether college student consumers always consider an obvious fact: money not spent now can be spent later.

In particular, we are interested in whether reminding students about this well-known
fact about money causes them to be a little thriftier. A skeptic might think that such a
reminder would have no impact. We can summarize these two perspectives using the null
and alternative hypothesis framework.

H0: Null hypothesis. Reminding students that they can save money for later purchases
will not have any impact on students' spending decisions.

HA: Alternative hypothesis. Reminding students that they can save money for later
purchases will reduce the chance they will continue with a purchase.

In this section, we'll explore an experiment conducted by researchers that investigates this very question for students at a university in the southwestern United States.

Frederick S, Novemsky N, Wang J, Dhar R, Nowlis S. 2009. Opportunity Cost Neglect. Journal of Consumer Research 36: 553-561.

One-hundred and fifty students were recruited for the study, and each was given the fol-
lowing statement:

Imagine that you have been saving some extra money on the side to make some
purchases, and on your most recent visit to the video store you come across a
special sale on a new video. This video is one with your favorite actor or actress,
and your favorite type of movie (such as a comedy, drama, thriller, etc.). This
particular video that you are considering is one you have been thinking about
buying for a long time. It is available for a special sale price of $14.99.
What would you do in this situation? Please circle one of the options below.

Half of the 150 students were randomized into a control group and were given the following
two options:
(A) Buy this entertaining video.
(B) Not buy this entertaining video.

The remaining 75 students were placed in the treatment group, and they saw a slightly
modified option (B):
(A) Buy this entertaining video.
(B) Not buy this entertaining video. Keep the $14.99 for other purchases.

Would the extra statement reminding students of an obvious fact impact the purchasing
decision? Table 2.4 summarizes the study results.

\begin{tabular}{lccr}
\hline
& buy DVD & not buy DVD & Total\\
\hline
control group & 56& 19 &75\\
treatment group& 41 &34 &75\\
\hline
Total & 97 & 53 & 150\\
\hline
\end{tabular}
Table: Summary of student choices in the opportunity cost study.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1 key:2a037c969d
## Summarizing opportunity cost (1)

Calculating summary statistics

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
library(dplyr)
opportunity <- data.frame(decision = c(rep('buyDVD',97),rep('nobuyDVD',53)),
  group = c(rep('control',56), rep('treatment',41), rep('control',19), rep('treatment',34)))
```

*** =sample_code
```{r}
# sample code
opportunity %>%
  group_by(group) %>%
  summarize(buy_prop = mean(decision == "buyDVD")) %>%
  mutate(buy_perc = 100*buy_prop)

```

*** =solution
```{r}
# solution code
opportunity %>%
  group_by(group) %>%
  summarize(buy_prop = mean(decision == "buyDVD")) %>%
  mutate(buy_perc = 100*buy_prop)

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:5774145f35
## Plotting opportunity cost

Barchart for the data

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
library(ggplot2)

opportunity <- data.frame(decision = c(rep('buyDVD',97),rep('nobuyDVD',53)),
  group = c(rep('control',56), rep('treatment',41), rep('control',19), rep('treatment',34)))

```

*** =sample_code
```{r}
# sample code

#can't figure out an easy way to put relative frequency (instead of count) on the y-axis
ggplot(opportunity, aes(x=decision, fill=group)) + geom_bar()

```

*** =solution
```{r}
# solution code

ggplot(opportunity, aes(x=decision, fill=group)) + geom_bar()
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:82803adc6c
## Randomizing opportunity cost

create a randomization distribution of the statistic which is the difference in proportions

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec

opportunity <- data.frame(decision = c(rep('buyDVD',97),rep('nobuyDVD',53)),
  group = c(rep('control',56), rep('treatment',41), rep('control',19), rep('treatment',34)))
```

*** =sample_code
```{r}
# sample code
set.seed(47)
opportunity_permute <- mosaic::do(10000)*opportunity %>%
  mutate(decision_perm = sample(decision)) %>%
  group_by(group) %>%
  summarize(buy_prop = mean(decision == "buyDVD"),
            buy_prop_perm = mean(decision_perm == "buyDVD")) %>%
  select(-group) %>%
  sapply(diff) # treatment - control
 

ggplot(opportunity_permute, aes(x=buy_prop_perm)) + geom_histogram(binwidth = .01) +
  geom_vline(aes(xintercept=buy_prop), col="red")

```

*** =solution
```{r}
# solution code
set.seed(47)
opportunity_permute <- mosaic::do(10000)*opportunity %>%
  mutate(decision_perm = sample(decision)) %>%
  group_by(group) %>%
  summarize(buy_prop = mean(decision == "buyDVD"),
            buy_prop_perm = mean(decision_perm == "buyDVD")) %>%
  select(-group) %>%
  sapply(diff) # treatment - control
 

ggplot(opportunity_permute, aes(x=buy_prop_perm)) + geom_histogram(binwidth = .01) +
  geom_vline(aes(xintercept=buy_prop), col="red")

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:a566675553
## Summarizing opportunity cost (2)

using the randomization distribution, compute the p-value

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec

opportunity_permute <- mosaic::do(10000)*opportunity %>%
  mutate(decision_perm = sample(decision)) %>%
  group_by(group) %>%
  summarize(buy_prop = mean(decision == "buyDVD"),
            buy_prop_perm = mean(decision_perm == "buyDVD")) %>%
  select(-group) %>%
  sapply(diff) # treatment - control
 
```

*** =sample_code
```{r}
# sample code

opportunity_permute %>%
 dplyr::summarise(sum(buy_prop > buy_prop_perm) / n())

```

*** =solution
```{r}
# solution code
opportunity_permute %>%
 dplyr::summarise(sum(buy_prop > buy_prop_perm) / n())

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:ecbd3d92c0
## Opportunity cost conclusion

What can we conclude (in words) given the analysis?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:VideoExercise lang:r xp:50 skills:1 key:445bbafcd6
## Errors and their consequences

Discussion of errors, how we make statistical conclusions (control type I error), our knowledge of which error comes from our decision not from truth (which we can't ever know)

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:c83d323545
## Different choice of error rate

What if we never want to make a type II error, what is our decision?  (Never reject)

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:068d39ca1d
## Errors for two-sided hypotheses

What are type I and type II errors for the TWO-sided hypotheses related to the opportunity costs example

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:NormalExercise lang:r xp:100 skills:1 key:fb0c78768f
## p-value for two-sided hypotheses: opportunity costs

compute the p-value for two-sided hypotheses, first compute the p-value for one tail of the distribution, then double that value to get the two-sided p-value. That's it!

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec

opportunity_permute <- mosaic::do(10000)*opportunity %>%
  mutate(decision_perm = sample(decision)) %>%
  group_by(group) %>%
  summarize(buy_prop = mean(decision == "buyDVD"),
            buy_prop_perm = mean(decision_perm == "buyDVD")) %>%
  select(-group) %>%
  sapply(diff) # treatment - control
```

*** =sample_code
```{r}
# sample code

opportunity_permute %>%
 dplyr::summarise(2*sum(buy_prop > buy_prop_perm) / n())

```

*** =solution
```{r}
# solution code

opportunity_permute %>%
 dplyr::summarise(2*sum(buy_prop > buy_prop_perm) / n())

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1 key:07b42ab6a1
## Hypotheses should be set *before* seeing data

Discussion / simulation on why we need to set the hypotheses first

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1 key:dd4166523b
## Error rates when snooping

Have them simulate data with snooping to see that their type I error rate doubles if testing two sided

Be honest with yourself:  will you look at big differences in the positive *and* negative directions?  If so, How big will your error rates be?  

Type I error is based on the null hypothesis being true (that is, our shuffled distribution being representative of the population).  If we consider both sides, then we naturally consider twice as many ``unusual'' situations as if we consider only one side of the null sampling distribution.  

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec

opportunity_permute <- mosaic::do(10000)*opportunity %>%
  mutate(decision_perm = sample(decision)) %>%
  group_by(group) %>%
  summarize(buy_prop = mean(decision == "buyDVD"),
            buy_prop_perm = mean(decision_perm == "buyDVD")) %>%
  select(-group) %>%
  sapply(diff) # treatment - control

```

*** =sample_code
```{r}
# sample code

opportunity_permute %>% 
  summarise(q.01 = quantile(buy_prop_perm, p = 0.01),
            q.99 = quantile(buy_prop_perm, p = 0.99))

opportunity_permute %>%
 dplyr::summarise(sum(-0.17333 > buy_prop_perm) / n())

opportunity_permute %>%
 dplyr::summarise(sum(0.17333 < buy_prop_perm) / n())

opportunity_permute %>%
 dplyr::summarise( (sum(-0.17333 > buy_prop_perm) + sum(0.17333< buy_prop_perm)) / n())

```

*** =solution
```{r}
# solution code
```

*** =sct
```{r}
success_msg("Great work!")
```

