---
title       : Introduction to Ideas of Inference
description : Lots of examples and big picture ideas about the logic of inference.  Does this show up on my github?

--- type:VideoExercise lang:r xp:50 skills:1 key:56b5302de6
## Welcome to the course!

Introduction and summary of ideas of inference.  In particular, what we assume is happening (the null hypothesis) and what we'd like to show (the alternative hypothesis).

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:c85be55b78
## Hypotheses (1)

Which would be a good null hypothesis for the example?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:bf6d293913
## Hypotheses (2)

Which would be a good alternative hypothesis for the example?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:VideoExercise lang:r xp:50 skills:1 key:c7e875bde0
## Randomized distributions

I'd really like a demo here (not in R).  Ones that I've seen before are at: http://www.rossmanchance.com/applets/ChiSqShuffle.html?FET=1 (click on show shuffle options); http://www.rossmanchance.com/applets/AnovaShuffle.htm?hideExtras=2 (click on show shuffle options); lots here: http://www.lock5stat.com/StatKey/index.html; or here: http://blog.revolutionanalytics.com/2014/10/statistics-doesnt-have-to-be-that-hard.html

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1 key:0d505087e1
## Randomly allocating samples

Use pre-code with either do() or sample() to have them create a handful of new samples taken from a null distribution

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
library(dplyr)
library(ggplot2)
library(NHANES)

#NHANES mimics a random sample of US residents

homes <- NHANES %>%
  select(MaritalStatus, HomeOwn) %>%
  filter(MaritalStatus %in% c("Married", "NeverMarried")) %>%
  filter(HomeOwn %in% c("Own", "Rent"))
  
set.seed(47)
homes %>%
  mutate(HomeOwn_perm = sample(HomeOwn)) %>%
  group_by(MaritalStatus) %>%
  summarize(prop_own = mean(HomeOwn == "Own"), 
            prop_own_perm = mean(HomeOwn_perm == "Own")) %>%
  select(-MaritalStatus) %>%
  lapply(diff) # NeverMarried - Married
  
```

*** =solution
```{r}
# solution code
library(dplyr)
library(ggplot2)
library(NHANES)

homes <- NHANES %>%
  select(MaritalStatus, HomeOwn) %>%
  filter(MaritalStatus %in% c("Married", "NeverMarried")) %>%
  filter(HomeOwn %in% c("Own", "Rent"))

set.seed(47)
homes %>%
  mutate(HomeOwn_perm = sample(HomeOwn)) %>%
  group_by(MaritalStatus) %>%
  summarize(prop_own = mean(HomeOwn == "Own"), 
            prop_own_perm = mean(HomeOwn_perm == "Own")) %>%
  select(-MaritalStatus) %>%
  lapply(diff) # NeverMarried - Married
  
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:9511617d95
## Randomization dotplot

using geom_dotplot visualize the distribution of the samples from the previous exercise

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code

set.seed(47)
shuffdiff <- mosaic::do(10)*homes %>%
  mutate(HomeOwn_perm = sample(HomeOwn)) %>%
  group_by(MaritalStatus) %>%
  summarize(prop_own = mean(HomeOwn == "Own"), 
            prop_own_perm = mean(HomeOwn_perm == "Own")) %>%
  select(-MaritalStatus) %>%
  lapply(diff) # NeverMarried - Married
  
ggplot(shuffdiff, aes(x=prop_own_perm)) + geom_dotplot()

```

*** =solution
```{r}
# solution code
set.seed(47)
shuffdiff <- mosaic::do(10)*homes %>%
  mutate(HomeOwn_perm = sample(HomeOwn)) %>%
  group_by(MaritalStatus) %>%
  summarize(prop_own = mean(HomeOwn == "Own"), 
            prop_own_perm = mean(HomeOwn_perm == "Own")) %>%
  select(-MaritalStatus) %>%
  lapply(diff) # NeverMarried - Married
  
ggplot(shuffdiff, aes(x=prop_own_perm)) + geom_dotplot()

```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:NormalExercise lang:r xp:100 skills:1 key:86b8b3fc6b
## Randomization histogram

using more samples and geom_histogram, create a full randomization distribution

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code

set.seed(47)
shuffdiff <- mosaic::do(1000)*homes %>%
  mutate(HomeOwn_perm = sample(HomeOwn)) %>%
  group_by(MaritalStatus) %>%
  summarize(prop_own = mean(HomeOwn == "Own"), 
            prop_own_perm = mean(HomeOwn_perm == "Own")) %>%
  select(-MaritalStatus) %>%
  lapply(diff) # NeverMarried - Married
  
  
ggplot(shuffdiff, aes(x=prop_own_perm)) + geom_density()  
```

*** =solution
```{r}
# solution code

set.seed(47)
shuffdiff <- mosaic::do(1000)*homes %>%
  mutate(HomeOwn_perm = sample(HomeOwn)) %>%
  group_by(MaritalStatus) %>%
  summarize(prop_own = mean(HomeOwn == "Own"), 
            prop_own_perm = mean(HomeOwn_perm == "Own")) %>%
  select(-MaritalStatus) %>%
  lapply(diff) # NeverMarried - Married
  
  
ggplot(shuffdiff, aes(x=prop_own_perm)) + geom_density()  
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:VideoExercise lang:r xp:50 skills:1 key:32c716a6af
## Using the randomization histogram

Discussion of what they did in R with the extension of the comparison of the null distribution (what they did) and the observed statistic value

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

--- type:NormalExercise lang:r xp:100 skills:1 key:3140c282c6
## Do the data come from the population?

sum(), count(), prop(), perc()  [all from mosaic]

*** =instructions
- instruction 1
- instruction 2

*** =hint
hint comes here

*** =pre_exercise_code
```{r}
# pec
```

*** =sample_code
```{r}
# sample code
ggplot(shuffdiff, aes(x=prop_own_perm)) + geom_density() + geom_vline(aes(xintercept=prop_own), col="red")
 
shuffdiff %>%
 dplyr::summarise(sum(prop_own > prop_own_perm) / n())
```

*** =solution
```{r}
# solution code

ggplot(shuffdiff, aes(x=prop_own_perm)) + geom_density() + geom_vline(aes(xintercept=prop_own), col="red")
 
shuffdiff %>%
 dplyr::summarise(sum(prop_own > prop_own_perm) / n())
```

*** =sct
```{r}
success_msg("Great work!")
```

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:6578e81ab0
## Conclusions

what can we conclude from the analysis?

*** =instructions
- option 1
- option 2
- option 3

*** =hint
hint

*** =pre_exercise_code
```{r}
# pec
```

*** =sct
```{r}
test_mc(2, feedback_msgs = c('wrong', 'right', 'wrong')) # if 2 is the correct option.
```

--- type:VideoExercise lang:r xp:50 skills:1 key:bd25a098e8
## Study Conclusions

Discussion of what we can and can't conclude based on the analysis above.

*** =video_link
//player.vimeo.com/video/154783078

*** =video_hls
//videos.datacamp.com/transcoded/000_placeholders/v1/hls-temp.master.m3u8

